Report - Latest Rodent Data

### 2018-12-01 evaluation.Rmd
Beginning the switch to portalcasting
Add portalcasting to package installs, use portalcasting functions to drive directory setup and modeling

model_metadata = yaml.load_file("data/model_metadata.yaml")
pred_interval = model_metadata$pred_interval
models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
species_names = portalr::FullPath('PortalData/Rodents/Portal_rodent_species.csv', '~') %>%
  read.csv(stringsAsFactors=FALSE, na.strings = '') %>%
  select(species = speciescode, full_species_name = scientificname)

@@

new_moon_file = portalr::FullPath('PortalData/Rodents/moon_dates.csv', '~')
new_moons = read.csv(new_moon_file)
new_moons$censusdate = as.Date(new_moons$censusdate)

>>>>

model_metadata = yaml.load_file("forecasting/data/model_metadata.yaml")
pred_interval = model_metadata$pred_interval
models_of_interest = c('AutoArima','Ensemble','ESSS','nbGARCH','pevGARCH')

species_of_interest = c('BA','DM','DO','PP','OT','NA','total')
species_names = portalr:::full_path('forecasting/PortalData/Rodents/Portal_rodent_species.csv', '~') %>%
  read.csv(stringsAsFactors=FALSE, na.strings = '') %>%
  select(species = speciescode, full_species_name = scientificname)

@@

new_moon_file = portalr:::full_path('forecasting/PortalData/Rodents/moon_dates.csv', '~')
new_moons = read.csv(new_moon_file)
new_moons$censusdate = as.Date(new_moons$censusdate)

### 2018-12-01 report.Rmd
Beginning the switch to portalcasting
Add portalcasting to package installs, use portalcasting functions to drive directory setup and modeling

# get most recent forecast prior to data collection
files = data.frame(names = list.files(path = './predictions', pattern = '*forecasts.csv'))
files$filedates = as.Date(substr(files$names,1,10),format='%Y-%m-%d')
latest_forecast = dplyr::filter(files,filedates<most_recent_date) %>% tail(1)

data = read.csv(paste('predictions/',latest_forecast$names,sep=''),na.strings = '')

>>>>

# get most recent forecast prior to data collection
files = data.frame(names = list.files(path = './forecasting/predictions', pattern = '*forecasts.csv'))
files$filedates = as.Date(substr(files$names,1,10),format='%Y-%m-%d')
latest_forecast = dplyr::filter(files,filedates<most_recent_date) %>% tail(1)

data = read.csv(paste('forecasting/predictions/',latest_forecast$names,sep=''),na.strings = '')
